A Spatial AR System for Wide-area Axis-aligned Augmentation of Planar Scenes in Industrial Settings

### 2021-07-05 paper/elsarticle/elsarticle-template.tex
paper

todo - maybe Hans would like to help?

>>>>

We evaluate our approach by considering the relative merits of augmenting 15 locations across the floorspace at the Pilotfabrik using our approach and two variants of a baseline approach. At each of the 15 locations, we aim to place an image aligned with the principal axes of the floorspace and such that the image appear in each instance to be free of projective distortions and to have the same dimensions, such that the horizontal axis of the image measure 30 cm.

 We carry out all steps of our approach within 15 minutes, which we set Our baseline in both instances calls for using the software bundled with the steerable mirror system mounted alongside our projector
